---
output:
  html_document: default
  pdf_document: default
---
Model Selection 
==============

```{r}
library(ISLR2)
# Baseball Database
summary(Hitters)
```

There are some missing values. So we need to remove them

```{r}
# Eliminate any row with missing values
Hitters=na.omit(Hitters)
with(Hitters, sum(is.na(Salary)))
```
Let's do Best Subset Regression 

```{r}
library(leaps)

# let's do subset regression
regfit.full=regsubsets(Salary~., data=Hitters)

summary(regfit.full)
```

- The models seems nested, but it's actually not. 
- It seems as it only picked up 8 features, let's do it in full 

```{r}
library(leaps)

# let's do subset regression
regfit.full=regsubsets(Salary~., data=Hitters, nvmax = 19)

reg.summary=summary(regfit.full)
# What is contained into Summary ( BIC, CP, RSS)
names(reg.summary)

# Plot the cp 
plot(reg.summary$cp, xlab = "Number of Variables", ylab = "Cp" )
which.min(reg.summary$cp)
points(10, reg.summary$cp[10], pch=20, col="purple")
```

It seems cp is the smallest with the model of 10 predictors. 


```{r}
# Y-axis: cp 
# Black indicates: Predictos IN, White: Predictors OUT 
plot(regfit.full, scale="Cp")
```

Notice that: 
- Bad CP's corresponded to models with all or none variables in it. 

```{r}
# get coeff
coef(regfit.full, 10)
```

- Gives you the coeff for the model with 10 variables.




